A proportional-integral-derivative (PID) controller is a feedback control loop mechanism. The aim is to reach a givenreference value (called set point) for the intput by regulating its output. The output $u(t)$ of the controller is thesum of three terms that are proportional conrrespondingly to the error $e(t)$ (P term), the integral of the error (Iterm) and the derivative of the error (D term). Each term is multiplied by a gain, $K_P$,$K_I$ and $K_D$ respectively,that will give their relative importance and fix the properties of the controller: undershoot, overshoot, responsetime, \ldots\begin{equation}	u(t) = K_P e(t) + K_I\int_0^t{e(\tau)d\tau} + K_D \frac{de(t)}{dt}\end{equation}The P term can be interpreted as a reponse to a perturbation. It is subject to a steady state error that reduces when$K_P$ rises. But increasing $K_P$ also enhances the oscillations of the system. Adding the I term removes the steadystate error as its action continue to affect the output as long as a stable state on the set point has not beenreached. The time to reach the set point is reduced when the gain of the integral term is increased but as for theproportional term it also enhances the oscillations and overshoots. Finally the derivative term acts as a predictiveterm by linear interpolation that help damping the oscillations%TODO high pass and low pass filters for the derivative term (see astrom-ch6)%TODO address integral windup%TODO address derivative kick%TODO feed forward when changing the setpoint%TODO think about a cascaded PID : the first controls the torque, the second control the motor: % motor_response = PID(measured_torque, PID(sensor, setpoint));%TODO look at the different forms of PID for optimisationThe controller described hereafter is able to drive the drone towards the desired attitude and linear velocity, the setpoints for this application. The inputs of the controller are the measurements of angular rates, linear velocity andattitude quaternion. The output are the torque and thrust that need to be applied on the model.  